Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-05-20 supplement/06_bat_data.Rmd
return to using recurse

  setorderv(dt, "time")
})
```

@@

```{r echo=FALSE, eval=TRUE}
# not shown or mentioned
fig_bat_res_timeseries <-
  ggplot() +
  geom_path(
    data = data_residence,
    aes(ts, resTime,
      colour = TAG
    ),
    show.legend = F
  ) +
  scale_color_brewer(palette = "Dark2") +
  scale_x_datetime() +
  ggthemes::theme_few() +
  labs(
    x = NULL,
    y = "residence time (mins)"
  )
```

```{r echo=FALSE}
# not shown or mentioned
# save to figures
ggsave(fig_bat_res_timeseries,
  filename = "supplement/figures/fig_bat_res_timeseries.png",
  dpi = 300,
  width = 6, height = 3
)
```

@@

We apply the residence patch method, using the default argument values (`lim_spat_indep = 100` (metres), `lim_time_indep = 30` (minutes), and `min_fixes = 3`). We change the `buffer_radius` to 25 metres (twice the buffer radius is used, so points must be separated by 50m to be independent bouts).

```{r}
# segment into residence patches
data_patches <- lapply(data_residence, atl_res_patch,
  buffer_radius = 25
)
```

>>>>

  setorderv(dt, "time")

  # print message when done
  message(sprintf("TAG %i residence times done", unique(dt$TAG)))
})
```

@@

@@

We apply the residence patch method, using the default argument values (`lim_spat_indep = 100` (metres), `lim_time_indep = 30` (minutes)). We change the `buffer_radius` to 25 metres (twice the buffer radius is used, so points must be separated by 50m to be independent bouts), and `min_fixes = 3`.

```{r}
# segment into residence patches
data_patches <- lapply(data_residence, atl_res_patch,
  buffer_radius = 25,
  min_fixes = 3
)
```
